Notes on Open Malaria

### 2018-11-22 documents/main.tex
updated
udpated

@@

>>>>

\section{What is Open Malria?}
Open malaria is for simulating malaria epidemology and the impacts on that epidemiology of interventions against malaria. 
 It is based on microsimulations of Plasmodium falciparum malaria in humans, originally developed for simulating malaria vaccines.
 These models simulate the dynamics of malaria parasitaemia in the course of an infection, of transmission, of immunity, and of the processes leading to illness and death. The system is set up to simulate malaria in village, or district size human populations

The original models were designed for simulating the impact of interventions acting on humans(for example, chemotherapy, or vaccines). OpenMalaria has subsequently been extended to include simulation of the dynamics of malaria in the mosquito vector, and of interventions that act on mosquitoes. It also offers alternative model structures for many of the components of the human models. The models allow for variations among humans in their exposure to mosquitoes, and in their responses to the parasite.

\section{Facts about Malaria}

\begin{itemize}
\item Endemic in 99 countries, 219 million cases, 660,000 deaths 
\item 90\% in Africa
\item Mortality rates fell by 26\% around the world in the past decade

@@

\subsection{Applied Interpretable Inference}
